cardinalR: Generating interesting high-dimensional data structures

### 2025-05-06 paper-cardinalR.Rmd
Added gen_cubehole

>>>>

The `gen_cubehole(n, p)` function generates a dataset of $n$ points sampled uniformly inside a cube, then removes points that fall within a central spherical hole, resulting in a hollow cube structure in $p$-dimensional space.

The initial points are drawn from a uniform cube centered at the origin: $X\_1, X\_2, X\_3 \sim \mathcal{U}(-0.5, 0.5)$.

The center of the cube is $(0, 0, 0)$. A spherical hole of radius $0.5$ is carved out by filtering out points whose Euclidean distance from the origin is less than or equal to $0.5$:

Remove if $\sqrt{X\_1^2 + X\_2^2 + X\_3^2} \leq 0.5$.

This results in a shell-like point cloud that fills the cube but avoids the spherical center.

For $p > 3$, Gaussian noise is added to the remaining dimensions (via `gen_unifcube()`):

$$
X\_j \sim \mathcal{N}(0, 0.05^2), \quad j = 4, \dots, p.
$$.
